\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-07 paper/sp.tex
figure
features are limited

As we operate these spectroscopic surveys,
the \gaia\ Mission has been revolutionizing our view of the disk.
It delivers good proper motions everywhere,
and extremely valuable parallax information
locally.
However, it does not deliver precise geometric parallaxes over a large fraction of
the disk, and certainly not in the dusty and crowded regions.
For these reasons, the value of \gaia\ in these infrared spectroscopy projects is not
to deliver distance information directly, but rather to calibrate stellar models,
which then deliver distance information through relationships between stellar
luminosities and spectral characteristics.

@@

Our position is that a methodological technique is correct inasmuch as
it delivers correct or best results \emph{under its particular assumptions}.
In that spirit, we present here the assumptions of the method
explicitly.
We will return to these assumptions in the Discussion section below,
to address the costs and benefits of each in more depth.
\begin{description}
\item[features] Perhaps our most fundamental assumption is that the parallax
of a star can be predicted from the features we provide, which are
the full set of (pseudo-continuum-normalized) pixels from the \apogee\ spectrum,
plus the $G$ and $(\BP-\RP)$ photometry from \gaia,
plus the $J$, $H$, and $K_s$ photometry from \zmass (\citealt{zmass}),
plus the $W_1$ and $W_2$ photometry from \wise.
That is, we assume that these spectrophotometric \emph{features} are sufficient
to predict the parallax in the face of variations in stellar
age, evolutionary phase, composition, and other parameters, and also interstellar
extinction.

@@

Because the \apogee\ target selection is based on \zmass (\citealt{zmass}),
every \apogee\ star also comes with \zmass\ photometry.
That is, for each star $n$,
we have \zmass\ near-infrared photometry $J_n$, $H_n$, and $K_n$.

@@

We need complete feature-vector information for all stars.  For this
reason, we define the Parent Sample to be the set of all stars that
meet the \apogee\ and \gaia\ cuts and also
have the complete set of photometry: $G_n$, $\BP_n$, $\RP_n$, $J_n$,
$H_n$, $K_n$, $W_{1n}$, and $W_{2n}$ and also an \apogee\ spectrum.
This Parent Sample contains ACE HOW MANY STARS? and is shown in \figurename~\ref{fig:parent}.
\begin{figure}
\caption{A visualization of the Parent Sample stars. The left panel
  shows a color--color diagram for all XXXX stars in the combined Parent Sample, colored by
  the \apogee\ pipeline estimates of surface gravity. The right
  panel shows small spectral segments of four example stars,
  chosen to span metallicity and surface gravity.\label{fig:parent}}
\end{figure}

@@

In that context: These features are bad! We could have used feature engineering
or an autoencoder to do a much better job. Definitely should do this in the future.

@@

>>>>

As we operate these spectroscopic surveys,
the \gaia\ Mission (CITE) has been revolutionizing our view of the disk.
It delivers good proper motions everywhere,
and extremely valuable parallax information
locally.
However, it does not deliver precise geometric parallaxes over a large fraction of
the disk, and certainly not in the dusty and crowded regions.
For these reasons, the value of \gaia\ in these infrared spectroscopy projects is not
to deliver distance information directly, but rather to calibrate stellar models,
which then deliver distance information through relationships between stellar
luminosities and spectral characteristics.

@@

Our position is that a methodological technique is correct inasmuch as
it delivers correct or best results \emph{under its particular assumptions}.
In that spirit, we present here the assumptions of the method
explicitly.
We will return to these assumptions in the Discussion section below,
to address the costs and benefits of each in more depth.
\begin{description}
\item[features] Perhaps our most fundamental assumption is that the parallax
of a star can be predicted from the features we provide, which are
the full set of (pseudo-continuum-normalized) pixels from the \apogee\ spectrum,
plus the $G$ and $(\BP-\RP)$ photometry from \gaia,
plus the $J$, $H$, and $K_s$ photometry from \zmass\ (\citealt{zmass}),
plus the $W_1$ and $W_2$ photometry from \wise.
That is, we assume that these spectrophotometric \emph{features} are sufficient
to predict the parallax in the face of variations in stellar
age, evolutionary phase, composition, and other parameters, and also interstellar
extinction.

@@

Because the \apogee\ target selection is based on \zmass\ (\citealt{zmass}),
every \apogee\ star also comes with \zmass\ photometry.
That is, for each star $n$,
we have \zmass\ near-infrared photometry $J_n$, $H_n$, and $K_n$.

@@

We need complete feature-vector information for all stars.  For this
reason, we define the Parent Sample to be the set of all stars that
meet the \apogee\ and \gaia\ cuts and also
have the complete set of photometry: $G_n$, $\BP_n$, $\RP_n$, $J_n$,
$H_n$, $K_n$, $W_{1n}$, and $W_{2n}$ and also an \apogee\ spectrum.
This Parent Sample contains ACE HOW MANY STARS? and is shown in \figurename~\ref{fig:parent}.
\begin{figure}
\includegraphics[width=\textwidth]{parent_sample.pdf}
\caption{A visualization of the Parent Sample stars. The left panel
  shows a color--color diagram for all XXXX stars in the combined Parent Sample, colored by
  the \apogee\ pipeline estimates of surface gravity. The right
  panel shows small spectral segments of four example stars,
  chosen to span metallicity and surface gravity.\label{fig:parent}}
\end{figure}

@@

One strong assumption of this work is that our set of features is sufficient to
build a predictive model for distance.
Our arguments for our included features is that they ought to be sufficient to
estimate a dust-independent apparent magnitude and the stellar parameters (especially
age and surface gravity) that are sensitive to luminosity.
The derived model parameters shown in \figurename~\ref{fig:spectral} do indicate that
the model is capturing some or all of this information.
However, our choice of features is very rigid:
In principle the data themselves should tell us what features to include.
In that direction, it would make sense to choose features using a more complex
technique like deep learning or an auto-encoder (CITE).
These methods generate good features automatically.
However, they also involve an enormous set of hyper-parameter-like choices,
and they involve sacrificing certain kinds of interpretability.
However, we expect that a better set of features would do better; in this sense
the project here is just a first step towards precise spectrophotometric distance
estimates.

@@

Complain about our lack of a noise model.
